---
title: "Week3"
author: "Justin Taylor"
date: "6/1/2018"
output: html_document
---

In week 2, we started a nuclear quantification for a primary hepatocyte experiment. We touched on how to read text files, data types, and plotting univariate data. First, we will read the entirety of the nuclear counts file with Nate's function, `readMolDev`. Next, we will read the metadata associated with these nuclear counts. Lastly, we can use the `dplyr` package to combine our data sources.

## Solutions to exercises  

```{r, echo=FALSE}
nucs <- readRDS("../Week2/inst/nuc_counts.RDS")
``` 

1. Print the first 15 lines of `nucs`.   

The second argument to `head` is `n`, which is the number of rows in the data frame that should be returned.  

```{r}
head(nucs, n = 15)
```

2. Print the last 10 lines of `nucs`.   

Note, we do not have to type the name of the argument (`n=10`), because the positions of the arguments match.

```{r}
tail(nucs, 10)
```

3. What is the data type of the well identifier in the `nucs` data? Change the type to `character`.

We can use the `as.` functions to change the data type of objects in R. `as.character` is the function that will change the data type to character, which typically works well for sample identifiers.  

```{r}
class(nucs$well)
nucs$well <- as.character(nucs$well)
```

4. Add a better x-label to the histogram we made, change the number of bars, and remove the main title from the plot  

By reading the documentation for `hist`, we see that `xlab` controls the label of the x-axis, and `main` is the title for the plot. `breaks` is the argument we can use for setting the number of bars in our histogram. 

```{r, fig.size=3, fig.height=4}
hist(nucs$nuc_count,
     xlab = 'Nuclear Count',
     main=NULL,
     breaks = 20)
```

## Week 3 Contents  

This week, we are going to start by reading a file of nuclear counts with a function, `readMolDev`. `readMolDev` is a function that Nate wrote to read imaging files. It is able to read an arbitrary number of plates and handles a variety of cases. 

```{r, echo=FALSE}
# readMolDev is bitching in RMarkdown - no tidyselect variables registered
nucs <- readRDS("inst/moldev-nucs.RDS")
```

## Reading scope data for multiple plates  

```{r, eval=FALSE}
library(magrittr)
library(tidyverse)
source("../Week2/R/readMolDev.R")
nucs <- readMolDev('../Week2/data/PAH0552-NucCounts.txt')
```
First, I typically print out the names of the fields in the data with `colnames`. 

```{r}
colnames(nucs)
```

Next, we should check out the first few rows to see that we have reasonable values for the fields we have identified.  

```{r}
head(nucs)
```

It is a good idea to inspect relevant variables one at a time. `unique` is a good function to identify the unique values in a vector. We can use `unique` to see that there are four plates for the run ID `PAH0552`. 

```{r}
unique(nucs$plate)
```

```{r}
unique(nucs$run)
```

We may want to see how many rows of data we have for each plate.  
```{r}
table(nucs$plate)
```

Visualizing the distribution of numeric variables is always a good idea. As we discussed last week, histograms are useful for visualizing the shape of a distribution. 

```{r, fig.width=4, fig.height=4}
hist(nucs$nuclear_count_transfluor,
     main = NULL,
     xlab = 'Nuclear count')
```

We can also use boxplots, which have the added benefit of providing a 5-number summary of the distribution (minimum, 1st quartile, median, 3rd quartile, max)

```{r, fig.height=4, fig.width=4}   
boxplot(nucs$nuclear_count_transfluor)
```

We can also see a numerical summary of the data by using the function `summary` on any numeric vector. The numbers you see below will match the boxplot above. 

```{r}
summary(nucs$nuclear_count_transfluor)
```

## Reading metadata 

Often, we need to read metadata that is stored as Excel files. The `openxlsx` package makes it easy to read a subset of a large Excel file. The `sheet` argument can either a sheet number or character that represents the name of the sheet in the actual Excel file. The `rows` argument is a numeric vector for the row indices we want to read. The default value for `colNames` is `TRUE`, which will cause the function to think the field names are in the first line (10351 in this case). We will look at the data and type these by hand today. 

```{r}
library(openxlsx)
meta <- read.xlsx('data/PAH sample database.xlsx', sheet = 'PAH',
                  rows=10351:10478, colNames=FALSE)
colnames(meta) <- c('study', 'sample_id',
                    'start_date', 'exp_type',
                    'culture_plate', 'culture_well', 
                    'cell_type', 'donor', 'phenotype',
                    'media', 'tx_cmpd', 'tx_conc', 
                    'tx_cmpd2', 'tx_conc2')
head(meta, 3)
```

If you ever need to access the sheet names in R, we can use a function `excel_sheets` from a package called `readxl`. 

```{r}
library(readxl)
excel_sheets('data/PAH sample database.xlsx')
```


## Merging data  

In general, there are four steps for combining data from two distinct sources. 

1. Identify fields that are shared between the two sets
2. Rename matching fields so they have the same name in both sets
3. Change data types of fields if necessary 
4. Choose the correct join to use

First, we should identify the intersection of fields for the two data sets. In this case, we know that each nuclear count in our data can be mapped to a single well on a plate. 

```{r}
colnames(nucs)
colnames(meta)
```

```{r}

```


## Regular expressions   


```{r}
first_plate <- read.delim('../Week2/data/PAH0552-NucCounts.txt',
                   skip = 8, nrows = 73-8)
tail(first_plate)
```

